Making Q-learning robust to time discretization

### 2019-01-17 paper/icml_drau/relatedworks.tex

Reinforcement learning has been studied from a mathematical perspective
when time and space are both continuous, in connection with optimal
control and the Hamilton--Jacobi--Bellman equation (a PDE which
characterizes the value function for continuous space-time). We refer to
\cite{cont_rl} and the references therein. In particular \TODO{cite
Munos, convergence of sol to HJB.}  The corresponding algorithms are
often impractical \cite{cont_rl} for larger-dimensional problems.
\cite{cont_rl} focusses on practical algorithms specific to the continuous
space-time case, including advantage updating.

>>>>

Reinforcement learning has been studied from a mathematical perspective
when time and space are both continuous, in connection with optimal
control and the Hamilton--Jacobi--Bellman (HJB) equation (a PDE which
characterizes the value function for continuous space-time). See for
instance
\cite{cont_rl,MunosBourgines98} and the references therein.
\cite{MunosBourgines98} use a grid algorithm to provably solve the HJB
equation when discretization tends to $0$. However,
the corresponding algorithms are
often impractical \cite{cont_rl} for larger-dimensional problems.
\cite{cont_rl} focusses on practical algorithms specific to the continuous
space-time case, including advantage updating.
